Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2022-03-09 Latex/journal_v2/version2/pr.tex
Add paper

\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
  \author{
    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
    \vspace{-.2cm}
  }
  }

@@

\subsection{Main Contributions}
In this paper, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we examine a single-cell downlink system involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
The system has a two-time scale and should be solved in two layers. On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, O-RU association and the assignment of PRB to UE in each slice is applied.
\item 
We consider three types of services that requires specific QoS: URLLC, which requires low latency and high reliability; eMBB, which needs high data rate; and mMTC, , which demand short-packet connectivity support for a massive number of low-power devices.
The problem of RAN slicing for different types of services is studied in this research.

\item 
We consider an intelligent resource allocation in the O-RAN architecture for the different services. Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing. So we must switch to machine learning and dynamic methods and find the most suitable approach.  
A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
 In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
by estimating of the gradient with respect to the parameters
of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
\end{itemize}
\section{Current State of the Research}
\subsection{System Model}
Assume we have $S$ preallocated slices serving $S$ services contains eMBB, URLLC, and mMTC services; There are $S_1$ slices for the first service type (eMBB), $S_2$ slices for the second service type (URLLC), and $S_3$ slices for the third service type (mMTC), , thus $S=S_1+S_2+S_3$.
Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
There are different application requests which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, a UE may be admitted and allocated to the resources.
Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs)  obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
Virtual network functions (VNFs) are functional blocks of the
system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.

In addition, there are $R$ multi-antenna RU that are shared between slices. Each RU $r \in \{1,2,...,R \}$
has $J$ antenna for transmitting and receiving data. Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k}|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from O-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}\label{eqI}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,l)}^{k} g_{u(s,l)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}^2 |\boldsymbol{h}_{r,{u(s,i)}}^k|^2 }_{\text{(quantization noise)}},
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}$ and $\gamma_{2} = e^{k}_{u(s,i)}e^{k}_{u(n,l)}$.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ O-RU.

@@

\mathcal{R}_{u(s_1,i)}^{e,r} &= \sum_{k=1}^{K_{s_1}} B \log_2({1+ \rho_{r,u(s_1,i)}^{k}})a_{u(s_1,i)} e^k_{r,u(s_1,i)},\\
\mathcal{R}_{u(s_1,i)}^{e} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_1,i)}^{e,r} 

@@

Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{j}^{th} $, $j \in \{2,3\}$ application of service type 2 (URLLC) and 3 (mMTC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated as follow

@@

\mathcal{R}_{u(s_2,i)}^{\mathfrak{u},r} &= \sum_{k=1}^{K_{s_2}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \zeta_{u(s_2,i)}^{k}){\beta}_{u(s_2,i)}^{k}, \quad \mathfrak{u} \in  \{u,m\} \\
\mathcal{R}_{u(s_1,i)}^{\mathfrak{u}} &= \sum_{r=1}^{R}\mathcal{R}_{u(s_2,i)}^{e,r} 

@@

where ${\beta}_{u(s_2,i)}^{k}=a_{u(s_2,i)} e^{k}_{u(s_2,i)}$
and $\zeta_{u(s_2,i)}^{k} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}^{k}}{N_{u(s_2,i)}^{k}}})$

@@

$C_{u(s_2,i)}^{k} = 1 - \frac{1}{(1+\rho_{u(s_2,i)}^{k})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}^{k}$ represents the blocklength of it. 

@@

In this part, the end-to-end mean delay for each service is obtained.
Suppose the mean total delay is depicted as $T_{\text{\text{tot}}}$,

@@

T^{\text{\text{tot}}} &=  T^{\text{proc}} + T^{tr} + T^{\text{pro}},\\
T^{\text{\text{proc}}} &=  T^{RU} + T^{DU} + T^{CU} + T^{UPF},\\
T^{tr} &= T^{fr,t} + T^{\text{mid},t} + T^{b,t},  \\
T^{\text{pro}} &= T^{fr,p} + T^{\text{mid},p} + T^{b,p}.  \\

@@

%{\color{red} I made a mistake and replaced pro with proc. Please correct them. Also, explain in more details the processing delay in this paragraph.}
%T_{\text{\text{tot}}} = T_{RU} + T_{front} + T_{DU} + T_{\text{mid}} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
The total delay ($T^{\text{\text{tot}}}$), is the sum of the processing delay ($T^{\text{proc}}$), the transmission delay ($T^{tr}$), and the propagation delay ($T^{\text{pro}}$). 
The propagation delay is the time takes for a signal to reach its destination. It obtains based on the length of the fiber link and the capacity of the link ($T = L/c$, where $L$ is the length of the link and c is the capacity of the link). The total propagation delay ($T^{\text{pro}}$), is the sum of the propagation delay in the fronthaul link $T^{fr,p}$, the midhaul link $T^{\text{mid},p}$, and the backhaul link $T^{b,p}$.
Also, the transmission delay is the amount of time required to push all the packets into the fiber link.
Moreover, it can formulated as 
$T = \frac{\mathcal{\alpha}}{R}$, where $R$ is the sum-rate of the packet transmission in each link and $\mathcal{\alpha}$ is the mean arrival data rate of each link.
So the total transmission delay ($T^{tr}$) is the sum of the transmission delay in the fronthaul $T^{fr,t}$, the midhaul $T^{\text{mid},t}$, and the backhaul $T^{b,t}$.
In this paper, we focus only on the processing delays to find the optimal number of VNFs, and we ignore the other two delays for simplification;
So, we assume that the total delay is approximate to the processing delay.
%Here we assume the propagation delay and the transmission delay are negligible compared to the processing delay.
T^{\text{\text{tot}}} \approx T^{\text{proc}}
\subsubsection{Processing Delay}

@@

Assume the mean arrival data rate of the UPF layer for slice $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$,

@@

T_{s}^{UPF} &= \frac{1}{\mu_s^u - \alpha_{s}/{M_s^{u}}},\\

@@

Moreover, $1/\mu_s^d$, $1/\mu_s^c$, and $1/\mu_s^u$ are the mean service time of the O-DU, O-CU, and the UPF layers, respectively.

@@

$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c, u\}$.

@@

So, the mean processing delay for UE $i$ in slice $s$ is 
T^{\text{proc}}_{u(s,i)} =  T^{RU}_{u(s,i)} + T^{DU}_{s} + T^{CU}_{s} + T^{UPF}_{s}.
Hence, for the simplification and focusing on the processing delay, we assume $T^{\text{\text{tot}}}_{u(s,i)} \approx T^{\text{proc}}_{u(s,i)} $.
%\subsection{Reliability of URLLC}
%As we know, UEs request URLLC services, require services with low latency.
%For the M/M/1 system, the probability of the delay for each application $s$ in the UPF, CU, DU and RU is as follow, respectively
%\begin{equation}
%\begin{split}
%P_r\{T_{UPF}^{s} \geq T_{UPF}^{max}\} &= e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}\\
%P_r\{T_{CU}^{s} \geq T_{CU}^{max}\} &= e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}\\
%P_r\{T_{DU}^{s} \geq T_{DU}^{max}\} &= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}\\
%P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} &= e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}\\
%\end{split}
%\end{equation} 
%So the probability of coincidence of these events is as follow
%\begin{equation}
%P_r\{E_1, E_2, E_3, E_4\} = A_1 A_2 A_3 A_4,
%\end{equation}
%where $E_1 = T_{UPF}^{s} \geq T_{UPF}^{max}$, $E_2 =T_{CU}^{s} \geq T_{CU}^{max} $, $E_3 =T_{DU}^{s} \geq T_{DU}^{max} $ and $E_4 =T_{RU}^{s} \geq T_{RU}^{max} $.
%Also $A_1=e^{-(\mu_u - \alpha_{s}/{M_s^{u}})T_{UPF}^{max}}$, $A_2=e^{-(\mu_c - \alpha_{s}/{M_s^{c}})T_{CU}^{max}}$, $A_3= e^{-(\mu_d - \alpha_{s}/{M_s^{d}})T_{DU}^{max}}$ and $A_4 = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}$.
\subsection{Physical Data Center Resource}
Each VNF requires
physical resources that include memory, storage, CPU and Network Bandwidth.
Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f \},
where $\bar{\Omega}_{s}^f\in \mathbb{C}^{4}$ and $\Omega_{M,{s}}^f, \Omega_{S,{s}}^f, \Omega_{C,{s}}^f, \Omega_{N,{s}}^f$ indicate the amount of required memory, storage, CPU and and Network Bandwidth, respectively.
Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in DU, CU and UPF is defined respectively as follows
&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d},\\
&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c},\\
&\bar{\Omega}_{\mathfrak{z},s}^{tot,u} = \sum_{f=1}^{M_{s}^u}\bar{\Omega}_{\mathfrak{z},s}^{f,u}, \\
$\forall \mathfrak{z} \in \{M, S, C, N\}$, where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ and $\bar{\Omega}_{\mathfrak{z},s}^{f,u}$ are the amount of resource that a VNF required in DU, CU and UPF, respectively. Then,
 \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}+\bar{\Omega}_{\mathfrak{z},s}^{tot,u}
Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
The amount of memory, storage, CPU and and Network Bandwidth is denoted by $\tau_{M_{j}}, \tau_{S_{j}}$, $\tau_{C_{j}} $ and $\tau_{N_{j}} $ for the $j^{th}$ DC, respectively
\begin{equation*}
\tau_j = \{\tau_{M_{j}}, \tau_{S_{j}}, \tau_{C_{j}}, \tau_{N_{j}} \},
\end{equation*}
In this system model, the assignment of physical DC resources to VNFs is considered. Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
\subsection{Power of the O-RU and the Fronthaul Capacity}
Let $P_r$ denote the power of the transmitted signal from the $r^{th}$ O-RU to UEs served by it. We have,
\begin{equation}\label{pr}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q}^2.
Since we have a fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}\label{cr}
C_{r} = \log{\left(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q}^2}\right)},
where $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q}^2$ is the power of quantization noise.
\subsection{Problem Statement}
%In this system, the goal is to minimize the cost of the system.
%The total power cost of O-RUs for transmitting data to UE is depicted as follow
%\begin{equation}
%P_{tot} = \sum_{r=1}^{R}P_r
%\end{equation}
Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
$\phi_{s}$. So the total power of the system for all active DCs that are connected to slices can be represented as
\begin{equation*}
\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .
\end{equation*}
where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,
  z_d =
    \begin{cases}
      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
      0 & \text{otherwise}
    \end{cases}       
Here, we assume that if any VNF placed in a server $d$ is used, the server is on and active, otherwise, it is off.
In addition, $\phi_{s}$ is obtained from below
\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively.
Here, we want to maximize the energy efficiency $\eta$. 
So the optimization problem is formulated as follow

@@

\text{subject to} \quad  &  P_r \leq P_{max} \quad \forall r
 \label{c11} \\
 &\mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
 &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,S,C, N\}, \label{c14}\\
&p_{r,u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
&p_{r,u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\

@@

& C_r \leq C^{max}_r \quad \forall r, \label{c15}\\ 
&T^{\text{\text{tot}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\

@@

& \sum_{r}g^r_{u(s,i)} = 1  \quad \forall s,\forall i, \label{c17}  \\
& \sum_{k =1}^{K_s} g^r_{u(s,i)} e^{k}_{r,u(s,i)} \geq 1  \quad \forall s,\forall i ,\forall r \label{c18-1} \\
& \sum_{s =1}^{S}\sum_{i=1}^{U_s}g^r_{u(s,i)} e^{k}_{r,u(s,i)} \leq 1  \quad \forall s,\forall i ,\forall r \label{c18} \\

@@

& g^r_{u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c20}  \\
& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}  

@@

\eqref{c11}, \eqref{c12} and \eqref{c12-1} indicate that the power of each O-RU does not exceed the maximum power, the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.  
Also, \eqref{c13} shows that the rate of each UE requesting each type of service, i.e., eMBB, mMTC, and uRLLC, is more than a threshold, respectively.

>>>>

\title{Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}
}
%
%\author{\IEEEauthorblockN{1\textsuperscript{st} Mojdeh Karbalaee Motalleb}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%mojdeh.karbalaee@ut.ac.ir}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Vahid Shah-Mansouri}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%vmansouri@ut.ac.ir}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Salar Nouri Naghadeh}
%\IEEEauthorblockA{\textit{Electrical and Computer Engineering} \\
%\textit{Tehran University}\\
%Tehran, Iran \\
%salar.nouri@ut.ac.ir}
%}
%%%%%  \author{
%%%%%    \IEEEauthorblockN{Mojdeh Karbalaee Motalleb}
%%%%%    \IEEEauthorblockA{School of ECE, College of Engineering, University of Tehran, Iran \\
%%%%%    Email: \{mojdeh.karbalaee\}@ut.ac.ir,
%%%%%    \vspace{-.2cm}
%%%%%  }
%%%%%  }

@@

\subsection{Main Contributions}
In this paper, as depicted in Figure \ref{fig:c11}, we aim at solving the problem of dynamic network slicing in the O-RAN system. 
Here, we examine a single-cell downlink system involving multiple network slices that share existing radio sources.
The main contributions of
this research are summarized as follow:
\begin{itemize}
\item 
The system has a two-time scale and should be solved in two layers. On a large-time scale, the problem of obtaining an optimal number of VNFs and the VNF placement is performed. Also, the assignment of PRB to the slices is obtained. On a small-time scale, the problem of power allocation, and the assignment of PRB to UE in each slice is applied.
\item 
We consider two types of services that requires specific QoS: URLLC, which requires low latency and high reliability; and eMBB, which needs high data rate.
The problem of RAN slicing for different types of services is studied in this research.

\item 
We consider an intelligent resource allocation in the O-RAN architecture for the different services. Since conventional models do not perform well here because of the heterogeneous QoS requirements of each service type and the complexity of dynamic RAN slicing. So we must switch to machine learning and dynamic methods and find the most suitable approach.  
A dynamic strategy of resource allocation is required to solve this problem to achieve the specific QoS for each type of service in the O-RAN architecture.
 In the small-time scale, the actor-critic algorithm such as DDPG is applied to the system that is based on control policy search. This method directly searches the optimal control policy
by estimating of the gradient with respect to the parameters
of the control policy. In the large-time scale, the deep Q-Network is implemented which is a value based algorithm and it can find best solution for discrete action-state.
\end{itemize}
\section{Current State of the Research}
\subsection{System Model}
Assume we have $S$ preallocated slices serving $S$ services contains eMBB, and URLLC services; We consider $S_1$ slices for the eMBB service type and $S_2$ slices for the URLLC service type. Therefore, we have $S=S_1+S_2$.
Each Service $s\in \{1,2,...,S\} $ consists of $U_{s}$ single-antenna user equipments (UEs) which require certain QoS to be able to use the requested program.
There are different application requests which fall into one of these service categories. Each application request requires specific QoS.
Assume each slice $s \in \{1,2,...,S \}$, consists of $K_{s}$, pre-allocated physical resource blocks (PRBs) obtained in the large-time scale, $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF. 
Virtual network functions (VNFs) are functional blocks of the system. Each VNF instance is running on a virtual machine (VM) using resources from the data centers. Each VM, requires enough resources of CPU, memory, storage and network bandwidth.
Moreover, we assume the system has $R$ single-antenna O-RU that serverd UEs cooperatively. Each O-RU $r \in \{1,2,...,R \}$ is transmitting and receiving the data of all UEs using the coordinated multipoint transmission (COMP) technology. Moreover, all O-RUs, have access to all PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ is obtained from
\begin{equation}\label{eq2}
\rho_{u(s,i)} =  \frac{\sum_{k=1}^{K_{s}}e_{u(s,i)}^k p_{u(s,i)}^{k}|{\bold{h}_{R,u(s,i)}^{H \: k}}|^2}{BN_0},
where $p_{u(s,i)}^{k}$ represents the transmission power allocated by O-RUs to $i^{th}$ UE served at slice $s$ on PRB $k$.
${\bold{h}_{R,u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from 
O-RUs to the $i^{th}$ UE in $s^{th}$ slice. 
Moreover, $e_{u(s,i)}^k \in \{0,1\}$ is a binary variable that illustrates whether PRB $k$ is assigned to the $i^{th}$ UE allocated to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise.
Moreover, we assume that each PRB is assigned to no more than one UEs. So we have
\sum_{s=1}^S \sum_{u=1}^{U_s} e_{u(s,i)}^k = 1

@@

\mathcal{R}_{u(s_1,i)} =  B \log_2({1+ \rho_{r,u(s_1,i)}}),

@@

Since the blocklength in URLLC and mMTC is finite, the achievable data rate for the $i^{th}$ UE request in the $s_{2}^{th} $, application of service type 2 (URLLC) is not achieved from Shannon Capacity formula. So, for the short packet transmission the achievable data rate is approximated as follow

@@

\mathcal{R}_{u(s_2,i)}^{\mathfrak{u}} =  B (\log_2({1+ \rho_{u(s_2,i)}})- \zeta_{u(s_2,i)}), 

@@

where $\zeta_{u(s_2,i)} = \log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{C_{u(s_2,i)}}{N_{u(s_2,i)}}})$

@@

$C_{u(s_2,i)} = 1 - \frac{1}{(1+\rho_{u(s_2,i)})^2}$ depicts the channel dispersion of UE  $i$ at slice $s_2$, experiencing PRB $k$ and
$N_{u(s_2,i)}$ represents the blocklength of it. 

@@

In this part, the mean processing delay for each service is obtained.
Suppose the mean processing delay is depicted as $T_{\text{\text{proc}}}$,

@@

T^{\text{\text{proc}}} =  T^{RU} + T^{DU} + T^{CU},

@@

@@

Assume the mean arrival data rate for each slice $s$ ($\alpha_{s}$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and the O-DU ($\alpha_{s}^D$). so $\alpha_{s} \approx \alpha_{s}^C \approx \alpha_{s}^D$,

@@

@@

Moreover, $1/\mu_s^d$, and $1/\mu_s^c$ are the mean service time of the O-DU, and O-CU layers, respectively.

@@

$s$ is $\alpha_{s}/{M_s^{i}}$ $ i \in \{d,c\}$.

@@

\subsection{Reliability of URLLC}
As we know, UEs request URLLC services, require services with low latency.
For the M/M/1 system, the probability of the delay for each application $s_2$ in the O-RU is as follow, 
\begin{equation}
P_r\{T_{RU}^{s} \geq T_{RU}^{max}\} = e^{-(R_{{tot}_s} - \alpha_{s})T_{RU}^{max}}
\end{equation} 
Also, we do not consider the reliability for O-CU and O-DU.
\subsection{Physical Data Center Resource}
Each VNF requires
physical resources that include memory, and CPU.
Let the required resources for VNF $f$ in slice $s$ is represented by a tuple as
\begin{equation}
\bar{\Omega}_{s}^f = \{\Omega_{M,{s}}^f, \Omega_{C,{s}}^f \},
\end{equation}
where $\bar{\Omega}_{s}^f\in \mathbb{C}^{2}$ and $\Omega_{M,{s}}^f, \Omega_{C,{s}}^f$ indicate the amount of required memory, and CPU, respectively.
Moreover, the total amount of required memory, storage, CPU and Network Bandwidth of all VNFs of a slice in O-DU, and O-CU is defined respectively as follows
\begin{equation}
\begin{split}
&\bar{\Omega}_{\mathfrak{z},s}^{tot,d} = \sum_{f=1}^{M_{s}^d}\bar{\Omega}_{\mathfrak{z},s}^{f,d},\\
&\bar{\Omega}_{\mathfrak{z},s}^{tot,c} = \sum_{f=1}^{M_{s}^c}\bar{\Omega}_{\mathfrak{z},s}^{f,c},\\
\end{split}
\end{equation}
$\forall \mathfrak{z} \in \{M, C\}$, where, $\bar{\Omega}_{\mathfrak{z},s}^{f,d}$, and $\bar{\Omega}_{\mathfrak{z},s}^{f,c}$ are the amount of resource that a VNF required in O-DU, and O-CU, respectively. Then,
\begin{equation}
 \bar{\Omega}_{\mathfrak{z},s}^{tot} = \bar{\Omega}_{\mathfrak{z},s}^{tot,d}+ \bar{\Omega}_{\mathfrak{z},s}^{tot,c}
\end{equation} 
Also, there are $D_c$ data centers (DC), serving the VNFs. Each DC contains several servers that supply VNF requirements.
The amount of memory, and CPU is denoted by $\tau_{M_{j}}$, and $\tau_{C_{j}} $ for the $j^{th}$ DC, respectively
\begin{equation*}
\tau_j = \{\tau_{M_{j}}, \tau_{C_{j}} \},
\end{equation*}
In this system model, the assignment of physical DC resources to VNFs is considered. Let $y_{s,d}$ be a binary variable indicating whether the $d^{th}$ DC is allocated the resources to the VNFs of $s^{th}$ slice or not.
\subsection{Problem Statement}
%In this system, the goal is to minimize the cost of the system.
%The total power cost of O-RUs for transmitting data to UE is depicted as follow
%\begin{equation}
%P_{tot} = \sum_{r=1}^{R}P_r
%\end{equation}
Assume the power consumption of baseband processing at each DC $d$ that is connected to VNFs of a slice $s$ is depicted as
$\phi_{s}$. So the total power of the system for all active DCs that are connected to slices can be represented as
\begin{equation*}
\textstyle \phi_{tot} = \sum_{s=1}^{S}\phi_{s} + \sum_{d=1}^{D_c}z_d \psi_d .
\end{equation*}
where, $z_d$ is shown that whether the $d^{th}$ DC is active or not and $\psi_d$ is a static cost when a DC is active, i.e.,
\begin{equation}
  z_d =
    \begin{cases}
      1 & \sum_{s=1}^{S}y_{s,d} \geq 1 \\
      0 & \text{otherwise}
    \end{cases}       
\end{equation}  
Here, we assume that if any VNF placed in a server $d$ is used, the server is on and active, otherwise, it is off.
In addition, $\phi_{s}$ is obtained from below
\begin{equation}
\phi_{s} = M_s^u \phi_s^u + M_s^c \phi_s^c+ M_s^d \phi_s^d
\end{equation}
where, $\phi_s^u$, $\phi_s^c$ and $\phi_s^d$ are the static cost of energy in UPF, CU and DU, respectively.
Here, we want to maximize the energy efficiency $\eta$. 
So the optimization problem is formulated as follow

@@

\text{subject to} \quad  & \mathcal{R}_{u_{(s,i)}} \geq  \mathcal{R}_{min}^{s} \quad \forall s, \label{c13} \\
 &\mathcal{R}_{u_{(s,i)}} \leq  \mathcal{R}_{max}^{s} \quad \forall s, \label{c13-1} \\
 &\textstyle \sum_{s=1}^{S} y_{s,d} \bar{\Omega}_{\mathfrak{z},s}^{tot}  \leq   \tau_{\mathfrak{z}_d}, \quad  \mathcal{E} = \{M,C\}, \label{c14}\\
&p_{u(s,i)}^{k}  \geq 0  \quad \forall i,\forall r,\forall s, \forall k,\label{c12} \\
&p_{u(s,i)}^{k}  \leq P_{s}^{max}  \quad \forall i,\forall r,\forall s, \forall k,\label{c12-1} \\

@@

&T^{\text{\text{proc}}}_{u(s,i)}  \leq T^{max}_{s} \quad \forall i,\forall s,\label{c16} \\

@@

& \sum_{s =1}^{S}\sum_{i=1}^{U_s} e^{k}_{u(s,i)} = 1  \quad \forall s,\forall i ,\forall r \label{c18} \\

@@

& e^k_{r,u(s,i)} \in \{0,1\} \quad \forall s,\forall i, \label{c21}\\  
& P_r\{T_{RU}^{s_2} \geq T_{RU}^{max}\} = e^{-(R_{{tot}_{s_2}} - \alpha_{s_2})T_{RU}^{max}}\label{c22-3}

@@

\eqref{c12} and \eqref{c12-1} indicate that the power of each UE is a positive integer value, and the power of each UE in each service does not exceed the maximum power of each service, respectively.  
Also, \eqref{c13} and \eqref{c13-1} shows that the rate of each UE requesting each type of service, i.e., eMBB, and URLLC, has a maximum and minimum, respectively.
\eqref{c16} expressed the limited end-to-end delay of the received signal, respectively.
